%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\usepackage{microtype}
\addbibresource{bibliography.bib}

\begin{document}
\header{Matti}{Jokitulppo}
       {Software Engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Espoo,
    Finland
    
    \href{mailto:melonmanchan@gmail.com}{melonmanchan@gmail.com}
    \href{https://mattij.com/}{https://mattij.com}
    \href{github.com/melonmanchan}{github.com/melonmanchan}
  \section{languages}
    native: finnish
    fluent: english
    intermediate: swedish
  \section{programming}
    JavaScript
    Node.js
    React
    Angular
    HTML5
    CSS3
    Sass
    Python
    C\#
    Java
    PHP
\end{aside}

\section{interests}

electronics, games \& game programming, embedded programming, robotics, linux, open source software, web development, music

\section{education}

\begin{entrylist}
  \entry
    {2016 -}
    {Master's Programme in Computer Science}
    {Aalto University}
    {Software Systems and Technologies study track}
  \entry
    {2012 - 2015}
    {Degree in Software Engineering}
    {JAMK University of Applied Sciences}
    {}
  \entry
    {2011}
    {Finnish Matriculation Examination}
    {Koulutuskeskus Salpaus, Nastola}
    {}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {11 2015 - }
    {Aalto University Learning Environments research group}
    {Developer}
    {\emph{Developing mobile and web applications and augmented reality solutions}}

  \entry
    {2014 - }
    {Nestronite OY, Jyväskylä}
    {Developer}
    {\emph{Designing and developing Jaxber, a multi-platform mobile application for collecting customer feedback.}}
    
    \entry
    {04 – 07 2015}
    {N4S@JAMK, Jyväskylä}
    {Developer}
    {\emph{Developing Contriboard, a modern web app for team collaboration.}}
  
  \entry
    {04 – 07 2014}
    {N4S@JAMK, Jyväskylä}
    {Junior developer}
    {\emph{Converting Tieto TOAS JavaEE framework packages from CentOS/RHEL Linux to Ubuntu.}}
    
\end{entrylist}

\section{applications}

\begin{entrylist}
  \entry
    {2015}
    {Soar}
    {\href{https://github.com/melonmanchan/sardroid}{https://github.com/melonmanchan/sardroid}}
    {Hybrid app for real-time peer-to-peer video calls and vision sharing with WebRTC. Made with Cordova/Angular/Ionic/Sass/HTML5}
  \entry
    {2015}
    {Contriboard}
    {\href{http://n4sjamk.github.io/contriboard/}{http://n4sjamk.github.io/contriboard}}
    {Single page app for real-time collaboration, developed with React/NodeJS/Express/MongoDB.}
  \entry
    {2015}
    {Android robot}
    {\href{https://github.com/melonmanchan/Android-Robot-V2}{https://github.com/melonmanchan/Android-Robot-V2}}
    {Arduino-powered robot that's controlled over Bluetooth LE via an Android app, made as my thesis project for JAMK. C++/Java.}

  \entry
    {2014}
    {Jaxber}
    {\href{http://jaxber.com}{http://jaxber.com}}
    {Multi-platform mobile application for collecting customer feedback, developed with HTML5/JavaScript/LESS utilizing PhoneGap framework. Also created management panel with Node.js/Express/Sass/Handlebars.js.}
  \entry
    {2013}
    {Tulospalvelu}
    {\href{https://bitbucket.org/teepalvelu/tulospalvelu}{https://bitbucket.org/teepalvelu/tulospalvelu}}
    {Website for tracking scores in team-based sports tournaments. PHP/JavaScript/HTML5}
\end{entrylist}


%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}

